Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-20 lloveras_2020.tex
tablas acomodadas.

While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \temp{(ver la region open en lat 0 y long 200)}. Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature. In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0  & 0&93 &(\Mi&12&9\%)  &   7&4 &(\Pl&~3&9\%) &   1&11 &(\Pl&20&7\%) \\
1  & 0&84 &(\Mi&11&3\%)  &   8&3 &(\Pl&15&3\%) &   1&30 &(\Pl&16&1\%) \\
2  & 0&74 &(\Mi&16&1\%)  &   8&9 &(\Pl&19&1\%) &   1&33 &(\Pl&14&2\%) \\
3  & 0&48 &(\Mi&12&5\%)  &   7&7 &(\Pl&10&5\%) &   0&98 &(\Pl&~5&7\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
CR-2082\\
1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
\hline          
CR-2208\\
1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

>>>>

While CR-2082 was highly axisymmetric and showed virtually no ARs (active region) \temp{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $310\mdeg$ \diego{and }. Except for these ARs, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature. In the AR, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature, that is why those ranges were excluded from the analysis.

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
CR-2082\\
I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
\hline          
CR-2208\\
I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}
